% -*- TeX-engine: xetex; eval: (auto-fill-mode 0); eval: (visual-line-mode 1); -*-
% Compile with XeLaTeX

%%%%%%%%%%%%%%%%%%%%%%%
% To do before class
%%%%%%%%%%%%%%%%%%%%%%%

% Print off Readiness Assessment 1

% Send email about registering clicker.
% Test run readiness assessment on iClicker.
% I need to get scratch off sheet from Mine.

% Send the Logistics/Week0Annoucnement (the night before).
% Send an email reminding students to bring a charged computer (the night before).

% Questions for Mine
% Can I get scratch off sheets.
% What do you do during group portion?
% Question: voluntary vs. non-response

%%%%%%%%%%%%%%%%%%%%%%%
% Option 1: Slides: (comment for handouts)   %
%%%%%%%%%%%%%%%%%%%%%%%

%\documentclass[slidestop,compress,mathserif,12pt,t,professionalfonts,xcolor=table]{beamer}
%
%% solution stuff
%\newcommand{\solnMult}[1]{
%\only<1>{#1}
%\only<2->{\red{\textbf{#1}}}
%}
%\newcommand{\soln}[1]{\textit{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Option 2: Handouts, without solutions (post before class)    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \documentclass[11pt,containsverbatim,handout,xcolor=xelatex,dvipsnames,table]{beamer}

 % handout layout
 \usepackage{pgfpages}
 \pgfpagesuselayout{4 on 1}[letterpaper,landscape,border shrink=5mm]

 % solution stuff
 \newcommand{\solnMult}[1]{#1}
 \newcommand{\soln}[1]{}

 % % This breaks things for me for some reason.
 % tell pgfpages how to set page sizes in XeLaTeX
 \renewcommand\pgfsetupphysicalpagesizes{%
    \pdfpagewidth\pgfphysicalwidth\pdfpageheight\pgfphysicalheight%
 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Option 3: Handouts, with solutions (may post after class if need be)    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[11pt,containsverbatim,handout,xcolor=xelatex,dvipsnames,table]{beamer}

% % handout layout
% \usepackage{pgfpages}
% \pgfpagesuselayout{4 on 1}[letterpaper,landscape,border shrink=5mm]

% % solution stuff
% \newcommand{\solnMult}[1]{\red{\textbf{#1}}}
% \newcommand{\soln}[1]{\textit{#1}}

% % % This breaks things for me for some reason.
% % % tell pgfpages how to set page sizes in XeLaTeX
% % \renewcommand\pgfsetupphysicalpagesizes{%
% %    \pdfpagewidth\pgfphysicalwidth\pdfpageheight\pgfphysicalheight%
% % }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Option 4: Notes Only
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% % See http://tex.stackexchange.com/questions/114219/add-notes-to-latex-beamer
% \documentclass[10pt,containsverbatim,xcolor=xelatex,dvipsnames,table,notes=only]{beamer}

% % handout layout
% \usepackage{pgfpages}
% \pgfpagesuselayout{2 on 1}[letterpaper, landscape, border shrink=5mm]

% % solution stuff
% \newcommand{\solnMult}[1]{#1}
% \newcommand{\soln}[1]{}

% % % Having a problem with this.
% % tell pgfpages how to set page sizes in XeLaTeX
% % \renewcommand\pgfsetupphysicalpagesizes{%
% %   \pdfpagewidth\pgfphysicalwidth\pdfpageheight\pgfphysicalheight%
% %}

%%%%%%%%%%
% Load style file, defaults  %
%%%%%%%%%%

\input{../../lec_style.tex}
\input{../../definitions_default.tex}
% ALT ALT
% \input{../../definitions_custom.tex}

%%%%%%%%%%%
% Cover slide info    %
%%%%%%%%%%%

\title{Unit 2: Probability and distributions}
\subtitle{2. Bayes' theorem and Bayesian inference}
\author{Sta 104 - Summer 2015}
\date{May 20, 2015}
\institute{Duke University, Department of Statistical Science}


%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin document and set Helvetica Neue font   %
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\fontspec[Ligatures=TeX]{Helvetica Neue Light}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Title Page

\begin{frame}[plain]

\titlepage
\vfill
{\scriptsize \webLink{\PersonalSite}{Dr. \LastName{}} \hfill Slides posted at  \webLink{\CourseSite}{\CourseSite}}
\addtocounter{framenumber}{-1} 

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Housekeeping}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Announcements}

\begin{itemize}

\item Review Project 1 assignment and start thinking about data you might want to find / collect for your project

\item Think carefully about what the population is and the cases in the population.  Do note use summary statistics for your data set.

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Main ideas}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Probability trees are useful for conditional probability calculations}
\label{mi1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{1. Probability trees are useful for conditional probability calculations}

\begin{itemize}

\item Probability trees are useful for organizing information in conditional probability calculations

\item They're especially useful in cases where you know P(A $|$ B), along with some other information, and you're asked for P(B $|$ A)

\end{itemize}

%---Note---%
\note{

Assigned one problem with prob tree to prepare for today.

Probability trees provide a way to organize information.  We use the rules of probability to fill in the tree (General addition rule, Bayes Theorem).

Probability trees are especially useful when trying to reverse the order of conditioning.

}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Bayesian inference: start with a prior, collect data, calculate posterior, make a decision or iterate}
\label{mi2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{2. Bayesian inference: start with a prior, collect data, calculate posterior, make a decision or iterate}

\begin{itemize}[<+->]

\item In Bayesian inference, probabilities are at times interpreted as \textbf{degrees of belief}.

\item You start with a set of \textbf{prior beliefs} (or prior probabilities).

\item You observe some data.

\item Based on that data, you update your beliefs.  

\item These new beleifs are called \textbf{posterior beliefs} (or posterior probabilities), because they are \textbf{post}-data.

\item You can iterate this process.

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Dice Game}

\begin{frame}
\frametitle{2. Bayesian inference: start with a prior, collect data, calculate posterior, make a decision or iterate}

\vfill

We'll play a game to demonstrate this approach...

\vfill

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Dice game}

\begin{itemize}

\item Two dice: 6-sided and 12-sided
\begin{itemize}
\item I keep one die on the left and one die on the right
\end{itemize}

\pause

\item The ``good die'' is the 12-sided die.

\pause

\item Ultimate goal: come to a class consensus about whether the die on the left or the die on the right is the ``good die''

\pause

\item We will start with priors, collect data, and calculate posteriors, and make a decision or iterate until we're ready to make a decision

\end{itemize}

%---Note---%
\note{

INSERT GOOD DIE IS THE ONE WITH HIGHER PROB OF GETTING 4 or MORE.

COST OF MAKING A MISTAKE.

COST OF PLAYING THE GAME FOR TOO LONG: You have to study this at home.

NEED A VOLUNTEER.  NOTE Taker.

Have them WALK THROUGH DECISION PROCESS.

Go to 40-60.

Pass around candy.

One nice aspect of this is that probabilities go like your brain is thinking.

}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Prior probabilities}

\begin{itemize}

\item At each roll I tell you whether you won or not (win = $\ge 4$)
\begin{itemize}
\item P(win $\mid$ 6-sided die) = 0.5 $\rightarrow$ bad die
\item P(win $\mid$ 12-sided die) = 0.75 $\rightarrow$ good die
\end{itemize}

\pause

\item The two competing claims are
\begin{itemize}
\item[] $H_1$: Good die is on left 
\item[] $H_2$: Good die is on right 
\end{itemize}

\pause

\item Since initially you have no idea which is true, you can assign equal \hl{prior probabilities} to the hypotheses
\begin{itemize}
\item[] P($H_1$ is true) = 0.5 
\item[] P($H_2$ is true) = 0.5 
\end{itemize}

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Rules of the game}

\begin{itemize}

\item You won't know which die I'm holding in which hand, left (L) or right (R). {\footnotesize left = YOUR left}

\pause

\item You pick die (L or R), I roll it, and I tell you if you win or not, where winning is getting a number $\ge$ 4. If you win, you get a piece of candy. If you lose, I get to keep the candy.

\pause

\item We'll play this multiple times with different contestants.

\pause

\item I will not swap the sides the dice are on at any point.

\pause

\item You get to pick how long you want play, but there are costs associated with playing longer.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Hypotheses and decisions}

\begin{center}
\renewcommand\arraystretch{1.25}
\begin{tabular}{l | c | c | }
  			&\multicolumn{2}{c|}{\hl{Truth}} \\
\cline{2-3}
\hl{Decision}		& {\small L good, R bad}		& {L bad, R good} \\
\hline
Pick L		& \hlGr{You get candy!}			& \red{You lose all the candy :(} \\
\hline
Pick R		& \red{You lose all the candy :(}	& \hlGr{You get candy!} \\
\hline
\end{tabular}
\end{center}

\vspace{0.75cm}

\hl{Sampling isn't free!} \\
At each trial you risk losing pieces of candy if you lose (the die comes up $<$ 4). Too many trials means you won't have much candy left. And if we spend too much class time and we may not get through all the material.
	
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Data and decision making}

\begin{center}
\renewcommand\arraystretch{1.25}
\begin{tabular}{l | c | c}
		& Choice (L or R)	& Result (win or loss) \\
\hline
Roll 1	& 				& 				\\
\hline
Roll 2	& 				& 				\\
\hline
Roll 3	& 				& 				\\
\hline
Roll 4	& 				& 				\\
\hline
Roll 5	& 				& 				\\
\hline
Roll 6	& 				& 				\\
\hline
Roll 7	& 				& 				\\
\hline
...		& 				& 				\\
\end{tabular}
\end{center}

\disc{What is your decision? How did you make this decision?}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% % ALT ALT 
% \subsubsection{Fair or Unfair?}

% \begin{frame}

%  \tableofcontents[currentsubsection]

% \end{frame}

% \begin{frame}
% \frametitle{Updating beliefs: coin flipping}

% \begin{itemize}[<+->]

% \item Two coins: a coin that is fair and one that lands heads up only 25\% of the time.

% \item I pick one of those coins, but do not tell you which one.

% \item Two competing claims:
% \begin{itemize}
% \item[] $H_1$: picked the unfair coin.
% \item[] $H_2$: picked the fair coin.
% \end{itemize}

% \item I flip the coin and tell you which side lands up.

% \item You update your beliefs with each flip.

% \item \webLink{https://stat.duke.edu/~jbw44/Teaching/Spring2015/post/R/u2_deck2.R.txt}{Demo in R}.

% \end{itemize}

% \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Posterior probability}

\begin{itemize}

\item \hl{Posterior probability} is the probability of the hypothesis given the observed data: P(hypothesis $|$ data)

\pause

\item Using Bayes' theorem
\begin{eqnarray*}
P(hypothesis \mid data) &=& \frac{P(hypothesis~and~data)}{P(data)} \\
\pause
&=& \frac{P(data~|~hypothesis) \times P(hypothesis)}{P(data)}
\end{eqnarray*}

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{}


\disc{Calculate the posterior probability for the hypothesis chosen in the first roll, and discuss how this might influence your decision for the next roll.}
% ALT ALT
% \disc{Calculate the posterior probability after flipping the coin once.}

% Set the overall layout of the tree
\tikzstyle{level 1}=[level distance=3.5cm, sibling distance=3.5cm]
\tikzstyle{level 2}=[level distance=3.5cm, sibling distance=1.5cm]

% Define styles for bags
\tikzstyle{bag} = [text width=4em, text centered]
\tikzstyle{end} = [minimum width=3pt, inner sep=0pt]

% Draw picture
\hspace{-1.5cm}
\begin{tikzpicture}[grow=right]
\node[bag] {}
    child {
        node[bag] {\emptybox{0.5cm}{0.25cm}      }  
            child {
                node[end, label=right:
                    {\emptybox{0.5cm}{0.25cm}      }] {}
                edge from parent
            }
            child {
                node[end, label=right:
                    {\emptybox{0.5cm}{0.25cm}      }] {}
                edge from parent
            }
            edge from parent
    }
    child {
        node[bag] {\emptybox{0.5cm}{0.25cm}      }        
            child {
                node[end, label=right:
                    {\emptybox{0.5cm}{0.25cm}      }] {}
                edge from parent
            }
            child {
                node[end, label=right:
                    {\emptybox{0.5cm}{0.25cm}      }] {}
                edge from parent
            }
            edge from parent
    };
\end{tikzpicture}


%---Note---%
\note{

Are your calculations making intuitive sense.

Show how to repeat.

Each person may have a different cost.  You may stop at different times.

}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Posterior probability and p-value do not mean the same thing}
\label{mi3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{3. Posterior probability and p-value do not mean the same thing}

\begin{itemize}

\item $\hl{p-value}:$ P(observed or more extreme outcome $|$ null hypothesis is true)
\begin{itemize}
\item This is more like P(data $|$ hyp) than P(hyp $|$ data).
\end{itemize}

\item $\hl{posterior}:$ P(hypothesis $|$ data)

\item Bayesian approach avoids the counter-intuitive Frequentist p-value for decision making, and more advanced Bayesian techniques offer flexibility not present in Frequentist models

\item \hl{Watch out!} \\
\begin{itemize}
\item $\hl{Bayes}$: A good prior helps, a bad prior hurts, but the prior matters less the more data you have.
\item $\hl{p-value}$: {It is really easy to mess up p-values}: \webLink{https://sakai.duke.edu/access/content/group/8d786209-ab9d-4d66-9a00-e138eaadd9c9/Articles/goodman-2008.pdf}{Goodman, 2008}

\end{itemize}

\end{itemize}

%---Note---%
\note{

Read start of paper on p-values.

}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{}

\vfill

\app{2.2 Bayesian inference for drug testing}{$\:$\\ See the \webLink{\CourseSite}{course website} for instructions. \\$\:$}

\vfill

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Summary of main ideas}

\vfill

\begin{enumerate}

\item \nameref{mi1}

\item \nameref{mi2}

\item \nameref{mi3}

\end{enumerate}

\vfill

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}